% Activate the following line by filling in the right side. If for example the name of the root file is Main.tex, write
% "...root = Main.tex" if the chapter file is in the same directory, and "...root = ../Main.tex" if the chapter is in a subdirectory.
 
%!TEX root =  mainMastersProject.tex

\chapter[Method: Simulations to Evaluate Bayesian Networks]{Creating Simulations to Evaluate Bayesian Networks.}

\section{Introduction}

The diagram below shows a general overview, each part of the process is discussed in more detail in the next sections.


\section{Setting up an Experiment}
An experiment consists of a simulation and reporters. Reporters are defined separately from the simulation because they are not inherent to it - they are defined with respect to what we want to know about the simulation.

\section{Creating a Bayesian Network from a Simulation Automatically}
The output of an experiment is a collection of runs, where each run is the global state of the simulation.

\section{Evaluating the Bayesian Network}

We want to evaluate different aspects of the Bayesian Network: structural criteria and performance criteria.

\subsection{Structural Criteria}
\begin{enumerate}
\item (temp) Events are ordered temporally - scenario-like.
\item (con) Evidence connects to hypotheses.
\item (exc) All events that are irrelevant are not included in the scenario BN.
\item (exh) All events that are relevant are included in the scenario BN.
\item (ind) Independent events are not connected to each other.
\end{enumerate}

\subsection{Performance Criteria}
\begin{enumerate}
\item The accuracy of the network is not lower than the inherent randomness of the simulation.
\item The strong view: probabilities in the network correspond exactly to probabilities in the simulation.
\item The weak view: Updates on evidence in the network go in the same direction as updates on evidence in the simulation.
\item Sensitivity analysis shows that no simulation-irrelevant event influences some output \footnote{rephrase}
\end{enumerate}

Now that we've established how the automatically generated Bayesian Networks are going to be judged


